High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-21 paper/paper.tex
fair to say I hate latex
trying to sort out reference
references sorted. Now starting writing

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

@@

\cite{abadie2002instrumental}

@@

\bibliography{paper/references}

>>>>

\author{%
  Patrick Altmeyer\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  We propose Conformal Counterfactual Explanations: an effortless and rigorous way to produce realistic and faithful Counterfactual Explanations for Black-Box models using Conformal Prediction. To address the need for realistic counterfactuals, existing work has primarily relied on surrogate models to learn the data-generating process. While this is an effective way to produce plausible counterfactual explanations, it effectively reallocates the task of learning realistic representations of the data from the model itself to the surrogate. Consequently, the generated explanations may look compelling to human inspectors but not necessarily accurately reflect the behaviour of the Black-Box model. Recent work has shown that instead of relying on surrogate models to generate plausible explanations, we can leverage predictive uncertainty for this task. Unfortunately, this approach works under the assumption that models can produce predictive uncertainty estimates. By leveraging a novel approach to differentiable Conformal Prediction we show that it is possible to relax that assumption.
\end{abstract}

@@

@@

\bibliographystyle{plain}
\bibliography{../bib}
